Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-06-29 WSSSPE2_report/WSSSPE2_review.tex
Use ASF abbreviation on first occurrence

The discussion on incentivizing those outside science focused on accessing the
well of affection that those working in software have for scientific research.
How can the interest and skills of this group be marshaled towards sustainable
contributions? There is evidence that the migration of scientific software
projects to the Apache Foundation has created opportunities for those not
employed in the scientific center to contribute to projects initiated by
scientists (especially where there is cross-over with industry needs, such as
provenance and workflow).

@@

Other (non-prize) forms of incentives are
\begin{itemize}
\item Converting reputation by joining the Apache Software Foundation, Google, etc.
\item Inviting ASF and open source people to contribute to scientific code (at
least on questions of overlapping
\item Template for assessing scientific contributions made through software.
\end{itemize}

@@

Journals should provide guidelines about what to consider when reviewing a
software submission. A good example for a relatively comprehensive guidelines
for reviewers (and thus in turn authors) are those of
JORS\footnote{\url{http://openresearchsoftware.metajnl.com/about/editorialPolicies}}.
Journals might also learn from organizations such as the Apache Foundation as to
what is good practice for software submissions. Guidance is needed on what
constitutes an incremental improvement that is significant enough to qualify for
publication, otherwise this assessment can be very subjective.

>>>>

The discussion on incentivizing those outside science focused on accessing the
well of affection that those working in software have for scientific research.
How can the interest and skills of this group be marshaled towards sustainable
contributions? There is evidence that the migration of scientific software
projects to the Apache Software Foundation (ASF) has created opportunities for those not
employed in the scientific center to contribute to projects initiated by
scientists (especially where there is cross-over with industry needs, such as
provenance and workflow).

@@

Other (non-prize) forms of incentives are
\begin{itemize}
\item Converting reputation by joining the ASF, Google, etc.
\item Inviting ASF and open source people to contribute to scientific code (at
least on questions of overlapping
\item Template for assessing scientific contributions made through software.
\end{itemize}

@@

Journals should provide guidelines about what to consider when reviewing a
software submission. A good example for a relatively comprehensive guidelines
for reviewers (and thus in turn authors) are those of
JORS\footnote{\url{http://openresearchsoftware.metajnl.com/about/editorialPolicies}}.
Journals might also learn from organizations such as the ASF as to
what is good practice for software submissions. Guidance is needed on what
constitutes an incremental improvement that is significant enough to qualify for
publication, otherwise this assessment can be very subjective.
